\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
% {{{
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{palatino}
\usepackage{multirow}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
% \usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.5cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
% }}}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small
        {
            \begin{minipage}
                {0.975\textwidth}\textbf{{\textsc{#1 \vphantom{p\^{E}} }}}
                \\[-0.3cm]
                \hrule
            \end{minipage}
            \\[-0.5cm]
        }
 }}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
    \textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} &  \\
%-----------------------------------------------------------

\begin{document}
{{{
% \hspace{0.5cm}\\
% \hspace{0.5cm}\\
% \hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\[-0.3cm]
}}}

\resheading{\textbf{\large WORK EXPERIENCE}}\\[\lsep] \\[-0.4cm]
% {{{
\begin{itemize}
\item \textbf{Goldman Sachs}  \\
    \emph{Intern} \hfill {\emph{(June 2013 - July 2013)}}
    \\[-0.6cm]

\item \textbf{Samsung Research \& Development} \\
    \emph{Software Developer}
    \hfill {\emph{(Jun 2014 - July 2015)}}
    \\ [-0.6cm]
\end{itemize}
\vspace{0.1cm}
% }}}

\resheading{\textbf{\large MASTER's THESIS \& RESEARCH PROJECTS}}\\[\lsep]
\\[-0.4cm]
%{{{
\begin{itemize}
\item \textbf{ Haskell Bounded Model Checking (HBMC)} \\ \emph{(Master's Thesis \& Seminar, Guided by Prof. Amitabha Sanyal)} \hfill {\emph{(December 2017 - present)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Objective: To write a tool that can statically prove assertions present in a given Haskell program up to some unrolling bound.
    \item The HBMC tool generates conditions for assertion failure from the given Haskell program.  These are then converted into SMTLib scripts and passed on to CVC4 (An SMTLib Solver).
    \item Major challenges for the upcoming future work are to speed up Type Inferencing,  fine tune Lazy Evaluation, implement support for Type Classes and Monads.
    \end{itemize}

\item \textbf{Security Analysis of Java using Datalog}
\\ {\emph{(R\&D Project, Guided by Prof. Amitabha Sanyal)}}\hfill{\emph{(July 2017 - December 2017)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Performed Intraprocedural points-to analysis for Java programs by writing the corresponding set of rules in Datalog.
    \item Obtained the initial set of predicates for the program, also known as program facts, using Doop, a framwork for Java pointer analysis written in Datalog.
    \end{itemize}

\item \textbf{Movie Recommendation Engine}\hfill{\emph{(July 2013 - June 2014)}}\\
 {\emph{B.Tech. Project (Guided by Prof. Anu Mary Chacko )}} 
    \\[-0.6cm]
 	\begin{itemize}\itemsep \isep
	\item Developed a system that retrieves user's movie ratings and likes from their social media profile
  	\item This data is used to find friends with similar movie taste as the User and to recommend movies.
	\end{itemize}
\end{itemize}	
% \pagebreak
\vspace{0.1cm}

\resheading{\textbf{\large ACADEMIC PROJECTS}}\\[\lsep] 
\\[-0.4cm]
%{{{
\begin{itemize}
\item \textbf{Headline Prediction from News Articles} \\
     \emph{(CS726: Advanced Machine Learning, Prof. Sunita Sarawagi)}
    \\[-0.6cm]

\item \textbf{Intelligent Carrom Playing Agent}
 \\ {\emph{(CS747: Foundations of Intelligent \& Learning Agents, Prof. Shivaram Kalyanakrishnan)}}
    \\ [-0.6cm]

\item \textbf{A study of ``Synthesizing data structure transformation from examples''}
 \\ {\emph{(CS613: Design \& Implementation of Functional Programming, Prof. Amitabha Sanyal)}}
    \\ [-0.6cm]

\item \textbf{Music Genre Classification}
 \\ {\emph{(CS725: Foundations of Machine Learning, Prof. Ganesh Ramakrishnan)}}
    \\ [-0.6cm]
    
\item \textbf{Latex Table manipulation}
 \\ {\emph{(CS 699: Software Lab, Prof. R.K Joshi)}}
     \\ [-0.6cm]

\item \textbf{Strongly Live Variable Analysis}
\\ {\emph{(CS 618: Program Analysis, Prof. Uday Khedkar)}}
    \\ [-0.6cm]

\end{itemize}
\vspace{0.1cm}

\resheading{\textbf{\large POSITIONS OF RESPONSIBILITY}}\\[\lsep] 
\\[-0.4cm]
%{{{
\begin{itemize}
    \item \textbf{Research Assistantship, IIT Bombay }\emph{(under Prof. D.B.Phatak)}\hfill {\emph{(Jul 2016-Present)}} \\[-0.6cm]
    \item \textbf{Placement Web Coordinator}\emph{(Placement Team, IIT Bombay)}\hfill {\emph{(Jul 2017-Jun 2018)}} \\[-0.6cm]
\end{itemize}

\vspace{0.1cm}
\resheading{\textbf{\large TECHNICAL SKILLS}} \\[\lsep] 
\\[-0.4cm]
%{{{
\begin{itemize}
  \item \textbf{Programming Languages}: Haskell, C, C++, Core Java, Datalog, Shell Scripting  \\[-0.6cm]
  \item \textbf{Tools}: Ansible, Git, \LaTeX, Beamer, Keras, Laravel, \\[-0.6cm]
\end{itemize}

\end{document}

