\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
% {{{
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{palatino}
\usepackage{multirow}
\fontfamily{SansSerif}
\selectfont
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
 %\usepackage{helvetica}
% \usepackage{array}
\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10in
\raggedbottom
% \raggedright
\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.5cm}
\renewcommand{\labelitemii}{$\circ$}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1.75in}
%\addtolength{\topmargin}{0.1375in}
%\addtolength{\textheight}{1.75in}
\pagestyle{empty}
% }}}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small
        {
            \begin{minipage}
                {0.975\textwidth}\textbf{{\textsc{#1 \vphantom{p\^{E}} }}}
                \\[-0.3cm]
                \hrule
            \end{minipage}
            \\[-0.5cm]
        }
 }}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
    \textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
% \textit{#3} &  \\
%-----------------------------------------------------------

\begin{document}
{{{
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\
\hspace{0.5cm}\\[-0.3cm]
}}}

% \indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
% \multirow{3}{*}{\huge\textsc{\textbf{Abhijeet Dubey}}}	& \textbf{Email:} \href{mailto:dubey.abhijeet09@gmail.com}{dubey.abhijeet09@gmail.com}				\\
% 							& \textbf{Website:} \href{https://github.com/dracarys09/}{github.com/dracarys09/}	\\
% 							& \textbf{Phone:} +91 9900190105
% \end{tabular*}

% \resheading{\textbf{\large Areas of Interest}}\\[\lsep] \\[-0.4cm]
% %{{{
%     \begin{itemize}
%     \item[] 
%     \hspace{-0.4cm} $\bullet$ Machine Learning 
%     \hspace{0.2cm} $\bullet$ Natural Language Processing
%   \hspace{0.2cm} $\bullet$ Algorithms
% \end{itemize}
% %}}}

% {\textbf{\large{ACADEMIC DETAILS}}}\\[\lsep]
% \\[0.2cm]
% \indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cccc}
% \hline
% \textbf{Degree}	&	\textbf{University}			&	\textbf{Year}	&	\textbf{CPI / \%}	\\
% \hline
% Post Graduation	&	IIT Bombay			&  2019	& 7.8 / 10		\\[0.15cm]
% Graduation	&	IIIT Jabalpur	& 2016	& 8.4 / 10		\\[0.15cm]
% %Intermediate/+2		&	CBSE				&  2012	 &	92.2 \%		\\[0.15cm]
% %Matriculation		&	CBSE					& 2010	&	9.2/10		\\
% \hline
% \end{tabular*}
% \\ \\

\resheading{\textbf{\large FIELDS OF INTEREST}}\\[\lsep] \\[-0.4cm]
% {{{
 \begin{itemize}
     \item Functional Programming, Algorithms, Machine Learning, Mathematical Logic
 \end{itemize}
% }}}
\vspace{0.5cm}

\resheading{\textbf{\large WORK EXPERIENCE}}\\[\lsep] \\[-0.4cm]
% {{{
\begin{itemize}
\item \textbf{Goldman Sachs}  \\
    \emph{Intern} \hfill {\emph{(June 2013 - July 2013)}}
    \\[-0.6cm]

\item \textbf{Samsung Research \& Development} \\
    \emph{Software Developer}
    \hfill {\emph{(Jun 2014 - July 2015)}}
    \\ [-0.6cm]
    \end{itemize}
% }}}
\vspace{0.5cm}
\resheading{\textbf{\large MASTER's THESIS \& RESEARCH PROJECTS}}\\[\lsep]
\\[-0.4cm]
%{{{
\begin{itemize}

\item \textbf{ Haskell Bounded Model Checking (HBMC)} \\ \emph{(Master's Thesis \& Seminar, Guided by Prof. Amitabha Sanyal)}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Objective: To write a tool that can statically prove assertions present in a given Haskell program upto some unrolling bound.
    \item Adopted Symbolic Execution with Bounded Model Checking approach in-line with CBMC: A Bounded Model Checker for C, C++ programs.
    \item The HBMC tool generates conditions for assertion failure from the given Haskell program.  These are then converted into SMTLib scripts and passed on to CVC4 (An SMTLib Solver).
    \item CVC4 will find and report an input for which the given program will fail or report that the assertion failure conditions are unsatisfiable.
    \item Major challenges for the upcoming future work are to speed up type Inferencing,  fine tune Lazy Evaluation, implement support for Type Classes and Monads.
    \end{itemize}

\item \textbf{Security Analysis of Java using Datalog}
\\ {\emph{(R\&D Project, Guided by Prof. Amitabha Sanyal)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep

    \item Performed Intraprocedural points-to analysis for Java programs by writing the corresponding set of rules in Datalog.
    \item Obtained the initial set of predicates for the program, also known as program facts, using Doop, a framwork for Java pointer analysis written in Datalog.
    \item Datalog is a declarative database query language with similar expressive power as SQL. 
    \item Using the analysis rules and program facts, Datalog performs the specified analysis and generates the results.

    \end{itemize}

\item \textbf{Movie Recommendation Engine}  \\
 {\emph{B.Tech. Project (Guide: Prof. Anu Mary Chacko )}} 
    \\[-0.6cm]
 	\begin{itemize}\itemsep \isep
	\item Developed a system that retrieves users movie ratings and likes from their social media profile
	\item The system fetches publicly available ratings and likes from the user's friends as well.
  	\item This data is used to find friends with similar movie taste as the User and to recommend movies.
	\end{itemize}
	
\end{itemize}
\vspace{0.5cm}
\resheading{\textbf{\large ACADEMIC PROJECTS}}\\[\lsep]
\\[-0.4cm]
%{{{
\begin{itemize}

\item \textbf{ Headline Prediction from News Articles} \\ \emph{(CS726: Advanced Machine Learning, Prof. Sunita Sarawagi)}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Modelled headline prediction task as monolingual machine translation and used SMT tool Moses for generating headlines from news articles.
    \item Used a dataset that consisted of 12 lac articles scraped from Times Of India.
    \item Used Facebook’s AI Research model:  Neural Attention Model for Abstractive Sentence Summarization(NAMAS) and Google’s Pointer Generator Network.
    \item Best results were produced by Pointer Generator Network which produced a BLEU score of \textbf{31.3}.
    \end{itemize}

\item \textbf{Intelligent Carrom Playing Agent}
\\ {\emph{(CS747: Foundations of Intelligent \& Learning Agents, Prof. Shivaram Kalyanakrishnan)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Implemented a model that can play carrom in both single player and 2 player setting.
    \item The agent was able to clear the board in 23.62 moves, averaged across 1000 runs.
    \end{itemize}

\item \textbf{A study of Synthesizing data structure transformation from examples}
\\ {\emph{(CS613: Design and Implementation of Functional Programming, Prof. Amitabha Sanyal)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Studied the paper “Synthesizing Data Structure Transformations from Input-Output Examples” by John K Feser, Swarat Chaudhuri and Isil Dillig.
    \item Studied the implementation of  2 learner for program synthesis from input output examples.
    \item Added new examples and recorded the results of 2 learner on these examples.
    \end{itemize}


\item \textbf{Music Genre Classification}
\\ {\emph{(CS725: Foundations of Machine Learning, Prof. Ganesh Ramakrishnan)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Aimed at classifying a given music track into genres such as Rock, Pop, and Classical.
    \item Used the GTZAN Genre Collection consisting of 1000 audio tracks.   It contains 10 genres, each represented by 100 tracks.
    \item Experimented with classifiers like Decision Tree, Random Forests and Multi-Class Neural Network to improve accuracy.
    \item Achieved an accuracy of \textbf{63.5\%} using only Timbral features.  This improves the original paper by \textbf{2.5\%}.
    \end{itemize}
    
\item \textbf{Latex Table manipulation}
\\ {\emph{(CS 699: Software Lab, Prof. R.K Joshi)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Developed a tool that takes in a latex file and a table number in the file as input and lets the user manipulate the said table.
    \item Manipulation functions include column-row swapping(transposing) and adding columns or rows.
    \end{itemize}
    
\item \textbf{Strongly Live Variable Analysis}
\\ {\emph{(CS 618: Program Analysis, Prof. Uday Khedkar)}}
    \\ [-0.6cm]
    \begin{itemize}\itemsep \isep
    \item Used program facts generated by Soot, a Java framework , to perform intra-procedural Strongly Live Variable analysis on a given program.
    \end{itemize}

\end{itemize}
\vspace{0.1cm}

\resheading{\textbf{\large POSITIONS OF RESPONSIBILITY}}\\[\lsep] 
\\[-0.4cm]
%{{{
\begin{itemize}
    \item \textbf{Research Assistantship, IIT Bombay }\emph{(under Prof. D.B.Phatak)}\hfill {\emph{(Jul 2016-Present)}} \\[-0.6cm]
        \begin{itemize}
                \item Responsible for mentoring a group of summer interns during May'17-Jul'17 and May'18-Jul'18.
                \item Responsible for writing deployment scripts of Collaborative Communities Portal using Ansible.
                \item Part of the interview panel and interviewed candidates for selection into Master's Program in IIT Bombay.
        \end{itemize}
    \item \textbf{Placement Web Coordinator}\emph{(Placement Team, IIT Bombay)}\hfill {\emph{(Jul 2017-Jun 2018)}} \\[-0.6cm]
        \begin{itemize}
                \item Updated and maintained 7-year-old legacy placement portal for 2017-18 placement season via necessary configuration changes.
                \item Developed new features according to the Placement Team policy in JSP with MySQL as backend.
                \item Performed several ad-hoc tasks like researching the technical feasibility of a new policy and maintaining the placement blog.
        \end{itemize}
\end{itemize}
\vspace{0.1cm}
%\hspace{0.5cm}
\resheading{\textbf{\large RELEVANT COURSEWORK}} \\[\lsep] \\
\\[-0.8cm]
%{{{
\begin{multicols}{2}
\begin{itemize}
  \item Functional Programming
  \item Algorithms and Complexity
  \item Combinatorics
  \item Program Analysis
  \item Artificial Intelligence
  \item Foundations of Machine Learning
  \item Intelligent and Learning Agents
  \item Advanced Machine Learning
\end{itemize}
\end{multicols}

%}}}
\vspace{0.2cm}

\hspace{0.5cm}\resheading{\textbf{\large TECHNICAL SKILLS}} \\[\lsep] \\
\\[-0.8cm]
%{{{
\begin{itemize}
  \item \textbf{Programming Languages}:Haskell, C, C++, Python, Java \\[-0.6cm]
  \item \textbf{Tools}: Git, Ansible, \LaTeX, Beamer, \\[-0.6cm]
\end{itemize}
%}}}
\vspace{0.2cm}

\resheading{\textbf{ \large INTERESTS AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Power-lifting, Reading, World Cinema.
\end{itemize}

\end{document}

